PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Few edits to user-study and conclusion + one reference.

\subsection{Scores and Scaling}
PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score. Since Lucene does't score on a pre-defined scale, we normalize all Lucene. Similarly, we normalize PageRanks. We normalize all scores on a per-query basis. This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers. By normalizing per-query, we do not penalize topics with a small number of papers.

@@

\begin{itemize}
	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined. We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm. Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples. It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples. We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
\end{itemize}

@@

To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas. We then manually picked weights that gave good results for all 6 topics.

@@

Figures \ref{relevance2} and \ref{reelvance3} show two different views of these data. The first plots the relevance ratio across all search engines. Relevance ratio is computed as (\# Highly Relevant + \# Moderately Relevant)/(\#Not Relevant). As we can see, PubCrawl has relevance ratio comparable to Google Scholar and Microsoft Academic Search. CiteSeer, on the other hand, has very poor relevance score since it produces a large number of non-relevant results. ACM Digital Library has the largest number of relevant documents in its results.

@@

\subsection{Challenges}
The main challenges with evaluating the user study were (1) Ground truth wasn't always clearly known, (2) Ground-truth is subjective, (3) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.

\section{Results}

User study results.

Some time comparisons.

@@

We observed that it is very difficult to find a scoring function that works well for all search queries. We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.

>>>>

\subsection{Scores and Scaling}
PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score. Since Lucene does't score on a pre-defined scale, we normalize all Lucene scores. Similarly, we normalize PageRanks too. All scores are scaled on a per-query basis instead of a per-corpus basis. This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers. By normalizing per-query, we do not penalize topics with a small number of papers.

@@

\begin{itemize}
	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined. We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm \cite{DBLP:conf/vldb/IlyasAE03}. Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples. It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples. We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
\end{itemize}

@@

To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas. We then manually picked weights that gave good results for all 6 topics. The settings we used for the user study were:  title weight (0.1), abstract weight (0), document weight (0.5), page rank (1).

@@

Figures \ref{relevance2} and \ref{relevance3} show two different views of these data. The first plots the relevance ratio across all search engines. Relevance ratio is computed as (\# Highly Relevant + \# Moderately Relevant)/(\#Not Relevant). As we can see, PubCrawl has relevance ratio comparable to Google Scholar and Microsoft Academic Search. CiteSeer, on the other hand, has very poor relevance score since it produces a large number of non-relevant results. ACM Digital Library has the largest number of relevant documents in its results.

@@

\subsection{Discussion}
Our preliminary user study only involved 4 topics and hence a larger study must be undertaken to rigorously study the quality of results. We also observed that: (1) quality of results depends heavily on the breadth of the search term (a narrow search term produces better results), (2) ground truth wasn't always clearly known, (3) ground-truth is subjective, (4) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications. Furthermore, the lack of non-ACM paper citations causes discrepancies in our PageRank algorithm compared to other search engines.

However, our preliminary user study shows that PubCrawl can find relevant documents and effectively tradeoff PageRank and text indexing scores.

@@

In this work, we built a publication search engine based on the PageRank algorithm and the Lucene text index. We adapted PageRank for the specific properties of the citation graph and indexed various paper attributes such as title, abstract and full text. We then explored multiple ways of combining the text indexing scores with PageRank. We observed that it is very difficult to find a scoring function that works well for all search queries. We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking. Our user study demonstrates that PubCrawl has a low false positive rate and produces a large number of moderately relevant results. However, it produces a low number of highly relevant results and there is potential to extend this work by finding better ranking functions.
